Test

### 2016-07-22 Berkeley_PD_Stop.Rmd
update

# Delete Other information from Disposition
OtherInformation <- c( "^M$" = "", ", M$" = "", "M, P$" = "", "P[, ]{0,2}" = "", "AR[, ]{0,2}" = "", "IN[, ]{0,2}" = "", "FC[, ]{0,2}" = "", "CO[, ]{0,2}" = "", "MH[, ]{0,2}" = "", "TOW[, ]{0,2}" = "", "0[, ]{0,2}" = "", "00000[, ]{0,2}" = "")
stop_df <- stop_df %>%
  mutate(Dispositions = str_replace_all(Dispositions, OtherInformation)) %>%
  mutate(Dispositions = str_replace_all(Dispositions, "[, ]{0,2}$", ""))

>>>>

# Remove Other information from Disposition
OtherInformation <- c( "^M$" = "", ", M$" = "", "M, P$" = "", "P[, ]{0,2}" = "", "AR[, ]{0,2}" = "", "IN[, ]{0,2}" = "", "FC[, ]{0,2}" = "", "CO[, ]{0,2}" = "", "MH[, ]{0,2}" = "", "TOW[, ]{0,2}" = "", "0[, ]{0,2}" = "", "00000[, ]{0,2}" = "")
stop_df <- stop_df %>%
  mutate(Dispositions = str_replace_all(Dispositions, OtherInformation)) %>%
  mutate(Dispositions = str_replace_all(Dispositions, "[, ]{0,2}$", ""))

# Creating new entries for multiple people in one disposition
